---
title: "How to Install neuroCombat"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Isaac Chen"
format: html
editor_options: 
  chunk_output_type: console
---

# Source:

- ComBat Harmonization: [https://github.com/Jfortin1/ComBatHarmonization](https://github.com/Jfortin1/ComBatHarmonization)

# Prerequisites:

- R version 4.X.X
  - For MacOS users: [https://cran.r-project.org/bin/macosx/](https://cran.r-project.org/bin/macosx/)
  - For Windows users: [https://cran.r-project.org/bin/windows/base/](https://cran.r-project.org/bin/windows/base/) 
- RStudio [https://posit.co/download/rstudio-desktop/](https://posit.co/download/rstudio-desktop/)
- Rtools [https://cran.r-project.org/bin/windows/Rtools/](https://cran.r-project.org/bin/windows/Rtools/) 
- Git [https://git-scm.com/](https://git-scm.com/)
- Link Git with RStudio:
  - Click on `Tools` > `Options` > `Git/SVN`
  - Under `Git Executable`, browse your folders to find the `git.exe` file.
    - For MacOS users: likely under `/user/local/bin/git`
    - For Windows users: likely under `C:/Users/[USERNAME]/AppData/Local/Programs/Git/bin/git.exe`

# Step-by-step installation guide:

## Step 1
```{r}
# Check if required packages are installed:
require("devtools")
require("BiocManager")
```

## Step 2
```{r}
# Download packages
#install.packages("devtools")
#install.packages("BiocManager")
```

## Step 3
```{r}
# Load libraries
library(devtools)
library(BiocManager)
```

## Step 4
When asked to `Update all/some/none? [a/s/n]:`, type `a` in console to update everything.

```{r}
# Download SummarizedExperiment via BiocManager
BiocManager::install("SummarizedExperiment")
```

## Step 5
When ask to `Enter one or more numbers, or an empty line to skip updates:`, type `1` to update everything.
```{r}
# Download neuroCombat example datase
install_github("jfortin1/neuroCombatData")
```

```{r}
# Download neuroCombat R package
install_github("jfortin1/neuroCombat_Rpackage")
```

## Step 6
```{r}
# Check if library can be called
library(neuroCombat)
library(neuroCombatData)
```

## Step 7
```{r}
# Load in sample data
seCorticalThickness <- seCorticalThickness

# Run ComBat on sample dataset
harmonized <- neuroCombat(
  dat = seCorticalThickness
  )
```

